### 2019-07-23 manuscript.tex
Update manuscript.tex

It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about to abolish than to intervene the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Yet, the progress of intervention is hindered due to the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple meanings with cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values and meanings attached to FGC is essential to comprehend the persistence of FGC practice \cite{}.  Social norm, as behavioural patterns that are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, is is crucial in intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

Convention theory, a widely regarded approach in FGC norm research, posited first that FGC was a marriageability convention and, latter on, a social norm and others, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.  The convention theory views FGC as a social behaviour resulting from group coordination \cite{Mack00, MackLeJe08}.  FGC was also viewed as a social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}. Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} and the bond within women's social networks could be interdependent and interconnected across generations  \cite{Mack00, ShelWand11}. \cfonly{add \cite{Bicc15}}.  Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.  For example, there was no coordination game observed in marital expectation \cite{EffeVogt15}.  it was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.  Studies showed that factors other than marriageability have underlined women’s fgc decisions \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.

@@

- descriptive norm:  what others do. In our case, is it fgc prevalence in a community?

@@

Changing social norm is a key step to changing behaviour  \cie{Bicc10}.  Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.  An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour. (using Tostan as an example) (also see \cite{Youn15}.  Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).  How to foresee a community conducive to certainty for girls without fgc?

>>>>

It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress in reducing FGC is not keeping up with the population growth: the number of girls and women undergoing FGC is projected to rise significantly over the next decade if current trends continue \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

In most part of the world, FGC is defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16}.  FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding values attached to FGC is essential to comprehend the persistence of FGC practice \cite{Bicc10}.  Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15} and widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a,MollRima10, RimaLapi15}, presents a crucial venue in comprehending intervention of sustainable changes \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

It was found that FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.  Social convention theory, a leading theory utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty as an important norm to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.   FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within women’s social groups \cite{ShelWand11}. The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.  Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.  Although normative behaviour based on convention theory was well documented regarding analysis of persistence of FGC practices (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), it was not without challenges \cite{EffeVogt15, Njam04}.  \cfonly{adding Bicchiori, The planned behaviour etc}For example, there was no coordination game observed in marital expectation \cite{EffeVogt15} and it was a peer convention for inclusion instead of for marriageability \cite{ShelWand11}.   It was also argued that anti-FGC discourse perpetuated a colonial assumption by universalizing a western view of normal body and sexuality \cite{Njam04}.  Studies showed that factors other than marriageability have underlined women’s  decisions of FGC \cite{AlcaGonz13, BellNova15, EffeVogt15, Hayf05, Mack09, PashPonn16, Rima08, ShelWand11, more?}.

@@

- descriptive norm:  what others do. In our case, is it fgc prevalence in a community?
- community level influence: “A daughter's adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community. Unexpectedly, a daughter's adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women.” \cie{GrosHayd19}

@@

Changes of social norms in public health beavhiors may require a few steps:  motivation, deliberation and action \cite{CislHeis18a}.  An alternative to fgc (a complete stop or a symbolic pricking) will have to provide motivation and facilitate the change of behaviour; the behavioural change will have to be a social action (i.e., gaining recognition and public participation within community) since fgc is a social norm;  and a public commitment to change in hope for reaching a critical mass needed to dismantle the normative behaviour. (using Tostan as an example) (also see \cite{Youn15}.  Promising change are observed in changing norms \cite{EvanSnid19} (and Tostan).  How to foresee a community conducive to certainty for girls without fgc?
